The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-02 Writeup/paper_v3.tex
Table entries in Sci. Notation and MI notation introduced

%More new commands by Arun Kannawadi
\newcommand{\mg}{\ensuremath{M_G}}
\newcommand{\mi}{\ensuremath{M_I}}
\newcommand{\sersicn}{S\'{e}rsic $n$ }
\newcommand{\sersic}{S\'{e}rsic }
\newcommand{\btt}{Bulge-to-Total }
\newcommand{\s}{\ensuremath{\mathcal{S}}}

@@

Major surveys such as the Hyper Suprime-Cam \citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DES;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} \citep{EuclidReport},
%(\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}),
Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
%(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_\text{F814W}$) space.}
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of $M_\text{F814W}$ for various flux-limited samples are plotted together. The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
   \label{fig:MIhist}
 \end{figure}

COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_\text{F814W}$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
\rachel{Actually, is this the catalog entry called ``MI''?  If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

At $M_\text{F814W}\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit. We obtain 97.84\% completeness in this bin for $M_\text{F814W}$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.

%We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
The region between $0.85<z<1.0$ is only moderately overdense and we do not seem to have as many underdense regions to compare with. It would rather be advantageous to disregard this region
and redo the volume limiting procedure.
We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We choose to impose the cut at $M_\text{F814W}=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin. This increases the sample size significantly, from 7,418 galaxies to 11,169. We call this sample \s$1$.

@@

Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve. Starting from $M_\text{F814W} = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9. 
As in the case of $M_\text{F814W}$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.

\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
\end{tabular}
\caption{List of different redshift bins, their environmental classification and the number of galaxies binwise for volume-limited samples constructed in three different ways: using hard luminosity cut (\s$1$), letting the luminosity cut evolve with redshift (\s$2$) and imposing stellar-mass cuts (\s$3$).}
\label{table:GalaxyCounts}
\end{table}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{Upper panel: Redshift distribution of volume-limited ($M_\text{F814W} <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_vollimited}
\end{figure}

@@

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs. \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins. \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways. \rachel{What are the 0 entries in this and other tables?  Just how close to zero are they?  Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.  Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}}
 \label{table:pvalues_all}
\end{table}

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & K-S & 0.00056 & 0.0001 & 0.0 \\
  All underdense    & A-D & 3e-5 & 1e-5 & 0.0 \\ \hline 
  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.9563 & 0.7476 & 0.5359 \\
  $z:[0.80,0.85]$ (OD) & A-D & 0.5162 & 0.3352 & 0.2290 \\ \hline
  $z:[0.65,0.75]$ (OD) vs & K-S & 0.00605 & 0.00025 & 0.00024 \\
  $z:[0.55,0.65]$ (UD) & A-D & 0.01201 & 0.00025 & 5e-5 \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the ellipticities computed using second moments are given for three cases: \emph{all} overdense (OD) vs. \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins. \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.  \rachel{Change numbers that are below 0.01 to scientific notation.}}
 \label{table:pvalues_momentbased_all}
\end{table}

%The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.

@@

Such a trend is also observed in axis ratios based on second moments. 
If $Q_{ij}$ represents the generic matrix element of the matrix of second moments, then define a complex number, sometimes known as the \emph{distortion}, as
\begin{equation}
 e = e_1 + ie_2 = \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}}.
 \label{eq:distortion}
\end{equation}
\arun{Is this the correct denominator?} \rachel{Yes.  There's another ellipticity definition with a different denominator, but we use distortion which is defined as in this equation.  (Once you read this response feel free to delete this conversation.)}
Then, one definition of ellipticity is the magnitude of this complex number which is $\sqrt{e_1^2+e_2^2}$.

>>>>

%More new commands by Arun Kannawadi
\newcommand{\mg}{\ensuremath{M_G}}
\newcommand{\mi}{\ensuremath{M_I}}
\newcommand{\sersicn}{S\'{e}rsic $n$ }
\newcommand{\sersic}{S\'{e}rsic }
\newcommand{\btt}{Bulge-to-Total }
\newcommand{\s}{\ensuremath{\mathcal{S}}}
\newcommand{\scinot}[2]{\ensuremath{#1 \times 10^{#2}}}

@@

Major surveys such as the Hyper Suprime-Cam \citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DES;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} \citep{EuclidReport},
%(\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}),
Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_AFTA_FINAL}
%(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_I$) space.}
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of $M_I$ for various flux-limited samples are plotted together. The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
   \label{fig:MIhist}
 \end{figure}

COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_I$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
\rachel{Actually, is this the catalog entry called ``MI''?  If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit. We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
Thus the sample $z\le1$ and $M_I<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_I<-22$, we are not affected by flux limit yet.

%We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
The region between $0.85<z<1.0$ is only moderately overdense and we do not seem to have as many underdense regions to compare with. It would rather be advantageous to disregard this region
and redo the volume limiting procedure.
We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin. This increases the sample size significantly, from 7,418 galaxies to 11,169. We call this sample \s$1$.

@@

Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve. Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9. 
As in the case of $M_I$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.

\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
 \hline
\end{tabular}
\caption{List of different redshift bins, their environmental classification and the number of galaxies binwise for volume-limited samples constructed in three different ways: using hard luminosity cut (\s$1$), letting the luminosity cut evolve with redshift (\s$2$) and imposing stellar-mass cuts (\s$3$).}
\label{table:GalaxyCounts}
\end{table}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_vollimited}
\end{figure}

@@

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | l | l | l | l | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs.  & \scinot{1.1}{-4} & \scinot{2.6}{-5} & \scinot{1.9}{-6} \\
  All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
  $z:[0.65,0.75]$ (OD) vs. & 0.613 & 0.431 & 0.231 \\
  $z:[0.80,0.85]$ (OD) & 0.494 & 0.237 & 0.130 \\ \hline
  $z:[0.65,0.75]$ (OD) vs. & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
  $z:[0.55,0.65]$ (UD) & \scinot{9.8}{-4} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (top) and Anderson-Darling (bottom) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs. \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins. \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
          The Anderson-Darling $p$-values are correct only upto 5 decimal places. 
% \rachel{What are the 0 entries in this and other tables?  Just how close to zero are they?  Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.  Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}
          }
 \label{table:pvalues_all}
\end{table}

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | l | l | l | l | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & \scinot{5.6}{-4} & \scinot{1.0}{-4} & \scinot{3.3}{-6} \\
  All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
  $z:[0.65,0.75]$ (OD) vs. & 0.9563 & 0.7476 & 0.5359 \\
  $z:[0.80,0.85]$ (OD) & 0.5162 & 0.3352 & 0.2290 \\ \hline
  $z:[0.65,0.75]$ (OD) vs & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
  $z:[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (top) and Anderson-Darling (bottom) obtained by comparing the ellipticities computed using second moments are given for three cases: \emph{all} overdense (OD) vs. \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins. \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.  \arun{Should I write only two significant digits for higher $p$-values?}
           The Anderson-Darling $p$-values are correct only upto 5 decimal places. }
 \label{table:pvalues_momentbased_all}
\end{table}

%The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
The Anderson-Darling test is carried out using the \texttt{adk} package\footnote{\url{http://www.inside-r.org/packages/cran/adk/docs/adk.test}} in \texttt{R}.

@@

Such a trend is also observed in axis ratios based on second moments. 
If $Q_{ij}$ represents the generic matrix element of the matrix of second moments, then define a complex number, sometimes known as the \emph{distortion}, as
\begin{equation}
 e = e_1 + ie_2 = \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}}.
 \label{eq:distortion}
\end{equation}
%\arun{Is this the correct denominator?} \rachel{Yes.  There's another ellipticity definition with a different denominator, but we use distortion which is defined as in this equation.  (Once you read this response feel free to delete this conversation.)}
Then, one definition of ellipticity is the magnitude of this complex number which is $\sqrt{e_1^2+e_2^2}$.
